---
title: "Analysis of Food Banks over COVID"
author: "Will Davidson"
format: pdf
---

```{r}
#### Preamble ####
# Purpose: Read in data from the Food Banks and make a
# graph of the number of people who used them before and after Covid
# Author: Will Davidson
# Email: davidsonwill200@gmail.com  
# Date: 3 February 2023

#### Workspace set-up ####
install.packages("opendatatoronto")
install.packages("lubridate")
install.packages("knitr")

library(knitr)
library(janitor)
library(lubridate)
library(opendatatoronto)
library(tidyverse)
```

```{r}
library(tidyverse) # A collection of data-related packages
library(janitor) # Helps clean datasets
```

```{r}
#### Acquire ####
food_banks <-
  # Each package is associated with a unique id  found in the "For 
  # Developers" tab of the relevant page from Open Data Toronto
  # https://open.toronto.ca/dataset/toronto-s-dashboard-key-indicators/
  list_package_resources("c6d64e9b-f85a-4084-be14-60cf18509203") |>
  # Within that package, we are interested in the 2021 dataset
  filter(name == 
    "Toronto progress portal - Key metrics") |>
  # Having reduced the dataset to one row we can get the resource
  get_resource()

write_csv(
  x = food_banks,
  file = "food_banks.csv"
)

head(food_banks)
```

```{r}
food_banks_clean <-
  clean_names(food_banks) |>
  select(measure_value, id, year) 

head(food_banks_clean)
```


```{r}
#### Explore ####
food_banks_clean <-
  clean_names(food_banks) |>
  slice(4018:4109) 

head(food_banks_clean)

write_csv(
  x = food_banks_clean,
  file = "cleaned_food_banks.csv"
)
```

```{r}
ggplot(data = food_banks_clean,
       mapping = aes(x = year,
                     y = measure_value))+
  geom_point(size=5)
  geom_line(colour = "red")
```

```{r}
ggplot(food_banks_clean, aes(year, measure_value))+
  geom_point(size=3)+
  geom_line(colour = "red")
```

```{r}
food_banks_clean %>%
  ggplot(aes(year, measure_value,
             colour = period_number_in_year))+
  geom_point(size = 3, alpha = 0.5)+
  geom_smooth(method = lm, se = F)+
  facet_wrap(~category)+
  labs(title = "Analysis of Food Banks")+
  theme_bw()
```




food_banks_clean <-
  clean_names(food_banks) |>
  select(measure_value, id, year) 

head(food_banks_clean)

food_banks_clean <-
  clean_names(food_banks) |>
  slice(8489:8551) 

head(food_banks_clean)

write_csv(
  x = food_banks_clean,
  file = "super_cleaned_food_banks.csv"
)
```{r}
super_cleaned_food_banks <- ggplot(food_banks_clean, aes(x = year, y = measure_value,
  colour = period_number_in_year))+
geom_point(size = 3, alpha = 0.5)+
geom_smooth(method = lm, se = F)+
facet_wrap(~category)+
labs(title = "Analysis of Community Housing- Individual")+
theme_bw()
```




```{r}
food_banks_clean <-
  clean_names(food_banks) |>
  select(measure_value, id, year) 

head(food_banks_clean)

food_banks_clean <-
  clean_names(food_banks) |>
  slice(8552:8614) 

head(food_banks_clean)

write_csv(
  x = food_banks_clean,
  file = "supered_cleaned_food_banks.csv"
)
  
super_cleaned_food_banks <-
ggplot(food_banks_clean, aes(year, measure_value,
  colour = period_number_in_year))+
geom_point(size = 3, alpha = 0.5)+
geom_smooth(method = lm, se = F)+
facet_wrap(~category)+
labs(title = "Analysis of Community Housing- Family")+
theme_bw()
```

```{r}
food_banks_clean <-
  clean_names(food_banks) |>
  select(measure_value, id, year) 

head(food_banks_clean)

food_banks_clean <-
  clean_names(food_banks) |>
  slice(1703:1867) 

head(food_banks_clean)

write_csv(
  x = food_banks_clean,
  file = "supersuper_cleaned_food_banks.csv"
)

super_cleaned_food_banks <-
ggplot(food_banks_clean, aes(year, measure_value,
  colour = period_number_in_year))+
geom_point(size = 3, alpha = 0.5)+
geom_smooth(method = lm, se = F)+
facet_wrap(~category)+
labs(title = "Average Home Price")+
theme_bw()
```





```{r}
installed.packages(github)
```








References

R Core Team (2022). R: A language and environment for statistical   computing. R Foundation 

for Statistical Computing, Vienna,   Austria. URL https://www.R-project.org/.

H. Wickham. ggplot2: Elegant Graphics for Data Analysis.
 
 Springer-Verlag New York, 2016.


